Caribou Demographic Projection - interesting & informative title TBD

### 2022-12-13 analysis/paper/paper.Rmd
More work on prior calibration

runScenarios = T 
doPriorCalibration=T
```
TO DO: build large table of all parameters as the various sections are written. Adjust UI for consistent terminology along the way.

@@

  #TO DO: move CaribouDemo_v1.15Reduce.R to paper directory. And produce pngs, rather than pdfs.
  source(here::here("analysis/scripts/calibratePriors.R"))
}else{
  KS<-read.csv(here::here("tabs/SurvKSAll.csv"))
}
  png(here::here("figs/PriorKSDists.png"),
    height = 4, width = fig_widths["two"], units = "in",res=600)
    base = ggplot(KS,aes(x=lse,y=KSDistance,color=sse))+
    geom_point()+facet_grid(scn~ssv,labeller="label_both",scales="free_y")+theme_bw()
    print(base)
  dev.off()

@@

```{r PriorKSDists, fig.cap="Prior parameter values should be set so that, given minimal monitoring data ('All' scenario: 1 year of 1 collar per year), the posterior survival distribution is similar to the distribution of simulated outcomes from the national model, measured here by Komogorov-Smirnov distance [ks.test function in @R_R_2022]. Low values of the mean and standard deviations of the prior distribution of the random effect of year on slope (sse=0.034784, ssv=0.01, $\\sigma^2_S$ in Table @ref(tab:priors)) meet this condition (Fig @ref(fig:priorAllFits). Priors should also be vague enough so that, given intensive monitoring of populations where survival is higher or lower than the national average ('High' and 'Low' scenarios: 15 years of 300 collars per year from 97.5% and 2.5% quantiles of the national model), posterior survival distributions reflect local survival, rather than priors from the national model. When the multiplier on the prior standard deviation of the survival intercept (lse: $\\beta^S_0$ in Table @ref(tab:priors)) is < 5, the prior is not sufficiently vague to meet the latter condition." , cache=TRUE}
knitr::include_graphics(here::here("figs/PriorKSDists.png"))

@@

```{r PriorAllFits, fig.cap="Differences between posterior distributions from the Bayesian model and simulated outcomes from the national model, assuming minimal monitoring (1 years of 1 collar per year) of populations from the 50% quantile of the national model. The multiplier on the prior standard deviation of the survival intercept ($\\beta^S_0$ in Table @ref(tab:priors)) is set to 5 in these examples.", cache=TRUE}
knitr::include_graphics(here::here("figs/SurvsQStarts1ssv0.01.png"))

@@

```{r PriorHighFits, fig.cap="Differences between posterior distributions from the Bayesian model and simulated outcomes from the national model, assuming intensive monitoring (15 years of 300 collars per year) of populations from the 97.5% quantile of the national model. The multiplier on the prior standard deviation of the survival intercept ($\\beta^S_0$ in Table @ref(tab:priors)) is set to 5 in these examples.", cache=TRUE}
knitr::include_graphics(here::here("figs/SurvsQStarts300highlse5.png"))

@@

>>>>

runScenarios = F 
doPriorCalibration=F #Note the prior calibration is time consuming. 
```
TO DO: build large table of all parameters as the various sections are written. Adjust UI for consistent terminology along the way.

@@

  #TO DO: move CaribouDemo_v1.15Reduce.R to paper directory. And produce pngs, rather than pdfs.
  source(here::here("analysis/scripts/calibratePriors.R"))
}else{
  KS<-read.csv(here::here("tabs/SurvKSAll.csv"))

}
  png(here::here("figs/PriorKSDists.png"),
    height = 4, width = fig_widths["two"], units = "in",res=600)
    base = ggplot(KS,aes(x=lse,y=KSDistance,color=sse))+
    geom_point()+facet_grid(scn~ssv,labeller="label_both",scales="free_y")+theme_bw()
    print(base)
  dev.off()

@@

```{r PriorKSDists, fig.cap="Prior parameter values should be set so that, given minimal monitoring data ('All' scenario: 1 year of 1 collar per year), the posterior survival distribution is similar to the distribution of simulated outcomes from the national model, measured here by Komogorov-Smirnov distance [ks.test function in @R_R_2022]. Low values of the mean and standard deviations of the prior distribution of the random effect of year on slope (sse=0.034784, ssv=0.01, $\\sigma^2_S$ in Table @ref(tab:priors)) meet this condition (Fig @ref(fig:priorAllFits). Priors should also be vague enough so that, given intensive monitoring of populations where survival is higher or lower than the national average ('High' and 'Low' scenarios: 15 years of 45 collars per year from 97.5% and 2.5% quantiles of the national model), posterior survival distributions reflect local survival, rather than priors from the national model. When the multiplier on the prior standard deviation of the survival intercept (lse: $\\beta^S_0$ in Table @ref(tab:priors)) is < 5, the prior is not sufficiently vague to meet the latter condition. Anthropogenic disturbance is set to 0 in these scenarios." , cache=TRUE}
knitr::include_graphics(here::here("figs/PriorKSDists.png"))

@@

```{r PriorAllFits, fig.cap="Differences between posterior distributions from the Bayesian model and simulated outcomes from the national model, assuming minimal monitoring (1 years of 1 collar per year) of populations from the 50% quantile of the national model. In these examples, the standard deviation the random effect prior (ssv: $\\sigma^2_S$ in Table @ref(tab:priors)) is 0.01, and  anthropogenic disturbance is 0.", cache=TRUE}
knitr::include_graphics(here::here("figs/SurvsQStarts1ssv0.01.png"))

@@

```{r PriorHighFits, fig.cap="Differences between posterior distributions from the Bayesian model and simulated outcomes from the national model, assuming intensive monitoring (15 years of 45 collars per year) of populations from the 97.5% quantile of the national model. In these examples, the multiplier on the prior standard deviation of the survival intercept (lse:$\\beta^S_0$ in Table @ref(tab:priors)) is 5 and  anthropogenic disturbance is 0.", cache=TRUE}
knitr::include_graphics(here::here("figs/SurvsQStarts45highlse5.png"))

@@

```{r PriorAllFitsAnthro90, fig.cap="Differences between posterior distributions from the Bayesian model and simulated outcomes from the national model, assuming minimal monitoring (1 years of 1 collar per year) of populations from the 50% quantile of the national model. In these examples, anthropogenic disturbance is 90%. When the multiplier on the prior standard deviation of the survival slope (bse: $\\beta^S_a$ in Table @ref(tab:priors)) is 3, the posterior survival distribution is similar to the distribution of simulated outcomes from the national model.", cache=TRUE}
knitr::include_graphics(here::here("figs/SurvsQStarts1Anthro90.png"))
```

```{r PriorHighFitsAnthro90, fig.cap="Differences between posterior distributions from the Bayesian model and simulated outcomes from the national model, assuming intensive monitoring (15 years of 45 collars per year) of populations from the 97.5% quantile of the national model. In these examples, anthropogenic disturbance is 90%, and the effect of anthropogenic disturbance varies from none (sS=0) through expected (sS=1) to double the expected slope (sS=2). All considered multipliers on the prior standard deviation of the survival slope (bse: $\\beta^S_a$ in Table @ref(tab:priors)) are sufficiently vague to reflect local variation among populations.", cache=TRUE}
knitr::include_graphics(here::here("figs/SurvsQStarts45Anthro90high.png"))
```
